### 2020-03-04 doc/icfp20/harmony.tex
harmony half done

TODO: Finish this.

@@

Their technique is to first require the melody notes to be members of
the harmonizing chords, then use their previous work to try to
create a harmonic analysis of every possible sequence of chords that
arises, choosing the one that most closely fits their
grammar. Although the result is not bad, it clearly leaves room for
improvement. Noted in the paper is that no attention is given to
voicing (how each of the four parts flows horizontally and how the
lines interact---in other words the counterpoint). Not noted is that
the melody note is always doubled, whereas typically in four-part
harmony it is preferred to double the root note. Also minimizing the
number of parse errors as a means to choose the best harmonization
does not necessarily have a musical meaning.

>>>>

As Piston does we require the harmonizing triad to include the melody
note. A function \texttt{harmonizations} is used to generate a list of
all candidate harmonizations for a given melody. For space
considerations the function is not shown here but is available in the
supplement \texttt{Harmony.agda}. Here again we encounter difficulties
with equality and membership. We use a bit vector to represent the
set of scale degrees in a triad where each scale degree is mapped to
an element of \texttt{Fin 7}.

We next restrict to progressions ending in a half cadence (V) to match
Piston's example. This results in 25 candidate progressions.

@@

Their technique is to first require the melody notes to be members of
the harmonizing chords, then use their previous work to try to create
a harmonic analysis of every possible sequence of chords that arises,
choosing the one that most closely fits their grammar. Although the
result is not bad, it clearly leaves room for improvement. Noted in
the paper is that no attention is given to voicing (how each of the
four parts flows horizontally and how the lines interact---in other
words the counterpoint). They use inversions (in which the
third or fifth of the chord is in the bass) to ensure each melody line
does not move too much, but as the harmonizing triads are all in close
postion separated from the melody the result sounds like a soprano
melody with block chord accompaniment rather than four independent
lines.

In addition note that the melody note is always doubled, whereas
typically in four-part harmony it is preferred to double the root note
as Piston does. Also minimizing the number of parse errors as a means
to choose the best harmonization does not necessarily have a musical
meaning.
